Fuzzy Extractors for Noisy Sources \\with More Errors Than Entropy

### 2015-02-11 constantRate/ConstCompFuzzExt-crypto.tex
put into Springer style

\documentclass[11pt]{article}
%\documentclass{llncs}
\def\shownotes{1}
\def\blinded{0}

\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsfonts}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{framed}
\usepackage{algpseudocode}

@@

@@

We augment the first construction with error-correcting codes to obtain our second construction, which works for \emph{sources with sparse high-entropy marginals}: sources over large alphabets for which sufficiently many symbols have high entropy individually, but no independence among symbols is assumed. In this construction, we use single symbols of $w$ for locking up bits of a secret that we then transform into $r$. This construction tolerates a higher error rate than the first construction, but over a larger alphabet, where errors may be more likely.

Our third construction provides information-theoretic, rather than computational, security. It works for \emph{sparse block sources}. These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous blocks. It uses symbols-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies existing fuzzy extractors to the resulting string.

@@

\begin{table}
\begin{center}
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline
Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\hline\end{tabular}
\end{center}
%end centering
\caption{Summary of new constructions.  }
\label{tab:upper bounds}
\end{table}

@@

It is seems plausible that in the real world (without random oracles), specific cryptographic hash functions, if used in this construction, will provide the necessary security~\cite[Section 3.2]{canetti2008obfuscating}, \cite[Section 8.2.3]{dakdoukThesis}. 
Moreover, Bitansky and Canetti~\cite{bitansky2010strong}, building on the work of~\cite{canetti2008obfuscating,CKVW10}, show how to obtain composable digital lockers based on a strong version of the Decisional Diffie-Hellman assumption without random oracles.

@@

\medskip
\paragraph{Organization }
The remainder of this paper is organized as follows: we cover notation and fuzzy extractors in \secref{sec:preliminaries}.  We present our information-theoretic construction in \secref{sec:info theory cons} and our two computational constructions in Sections \ref{sec:sampling} and \ref{sec:cor construction}.

@@

\paragraph{Sources with High-Entropy Samples}
Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$. For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$(\eta, \subsetEntropy)$-high-entropy samples} if $\Hav(w_{j_1}, \dots, w_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$. This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$. However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate.

A distribution obtained by applying short-output condensers multiple times to a single sample from a high-entropy source (e.g., via random projections) will have this property, because the outputs of the condensers will be contain fresh entropy as long as the total amount of entropy in the source is not exceeded
(by a simple conditional entropy argument---each subsequent element in the sequence $w_{j_1}, \dots, w_{j_\eta}$ will extract fresh entropy as long as fresh entropy remains conditioned on the previous elements).

\paragraph{The Construction}
The construction first chooses a random $r$ to be used as the output of the fuzzy extractor. It then samples a random subset of symbols $v_1=w_{j_1},..., w_{j_\eta}$ and creates a digital locker that hides $r$ using $v_1$ (We present and analyze the construction with uniformly random subsets; however, if necessary, it is possible to substantially decrease the required public randomness and the length of $p$ by using more sophisticated samplers. See~\cite{goldreich2011sample} for an introduction to samplers.) This process is repeated to produce $\ell$ digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively. The use of the composable digital lockers allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$.  Composability also allows reusability.

\begin{construction}[Sample-then-Obfuscate]
\label{cons:sampling}
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source with $(\eta, \subsetEntropy)$-high-entropy samples, where each $W_j$ is over $\mathcal{Z}$.  Let $\ell$ be a parameter, to be determined later. 
Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for the family of digital lockers with $\kappa$-bit outputs. Define $\gen, \rep$ as:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $r \overset{\$}\leftarrow \zo^\kappa$.
\item For $i=1,..., \ell$:
\begin{enumerate}[(i)]
\item Choose uniformly random distinct $1\le j_{i, 1},..., j_{i, \eta}\le \gamma$
\item Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
\item Set $\rho_i = \mathcal{O}(I_{v_i, r})$.
\item Set $p_i = \rho_i, (j_{i, 1},..., j_{i, \eta})$.
\end{enumerate}
\item Output $(r, p)$, where $p=p_1\dots p_\ell$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w'=w_1',..., w_\gamma', p = p_1\dots p_\ell)$
\item For $i=1,..., \ell$:
\begin{enumerate}[(i)]
\item Parse $p_i$ as $\rho_i, (j_{i, 1},..., j_{i, \eta})$.
\item Set $v_i' = w_{j_{i, 1}}',..., w_{j_{i, \eta}}'$.
\item Set $\rho_i(v_i') = r_i$.  If $r_i\neq \perp$ output $r_i$.
\end{enumerate}
\item Output $\perp$.
\end{enumerate}
\vspace{0.37in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\iffalse
\subsection{More errors than entropy?}
In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.  The structure of the partial block source implies that $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.  We assume that $\Hoo(W) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) \ge t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.

\textbf{Notes:} \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.  However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.

In the analysis of \consref{cons:sampling} we restricted our attention to partial block sources, to allow for an easy comparison with \consref{cons:info theoretic}.  However,  in fact \consref{cons:sampling}  is secure for any source where sampling produces a high entropy string~(entropy $\omega(\log n)$) with overwhelming probability. For example, it is secure for sources with symbols that are $\omega(\log n)/\log |\mathcal{Z}|$-wise independent.

\fi

\section{Construction for Sources with Sparse High-Entropy Marginals}
\label{sec:cor construction}
\lnote{stopped here; also need to reorder appendices}
In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.  Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of the output.

Before presenting the construction we provide some definitions from error correcting codes.
We use error-correct codes over $\{0,1\}^\gamma$ which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
Codes with $2^{\Theta(\gamma)}$ codewords and $t = \Theta(\gamma)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).  These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
}
\begin{definition}
\label{def:hamming z channel}
For a point $c\in \zo^\gamma$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
\end{definition}

\begin{definition}
Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.  Then a set $C$~(over $\zo^\gamma$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\decode$ such that $\Pr_{c\in C}[\exists c'\in \neigh_t(c) \text{ s.t. } \decode(c') \neq c] \leq \delta_{code}$.
\end{definition}
\bnote{these are quite strange.  changing them for dissertation.  update if accepted.}

\begin{construction}
\label{cons:first construction}
Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.  Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.  Let  $C\subset \zo^\gamma$ be an error-correcting code.
We describe $\gen, \rep$ as follows:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $c\leftarrow C$.
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item If $c_j = 0$: $p_j = \mathcal{O}(I_{w_j})$.
\item Else: $r_j \overset{\$}\leftarrow \mathcal{Z}$.
\subitem Let $p_j = \mathcal{O}(I_{r_j})$.
\end{enumerate}
\item Output $(c, p)$, where $p=p_1\dots p_\gamma$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item If $p_j(w_j') = 1$: set $c_j' = 0$.
\item Else: set $c_j' = 1$.
\end{enumerate}
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.15in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.  By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function. Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols. This restriction on the distribution is captured in the following definition.

\begin{definition}
\label{def:block guessable}
Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
\begin{cases}
1 & w_j = w_j'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1| ... |W_\gamma$ is a $(q, \alpha, \beta)$-\emph{unguessable block source} if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
\[
\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

We show some examples of unguessable block sources in \apref{sec:characterize}.  In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all blocks may arbitrarily correlated) is an unguessable block source~(\clref{cl:all blocks entropy}).

Unfortunately, \consref{cons:first construction} is not a computational fuzzy extractor.  The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).  However, we can show that $c$ looks like it has entropy.  We use the notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon_{sec}$.
\end{definition}
We now define a weaker object that outputs computational entropy~(instead of a pseudorandom key).  We call this object a computational fuzzy conductor.  It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\begin{definition}
\label{def:comp fuzzy cond}
A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
\begin{itemize}
\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{sec}, s_{sec}}(R |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}
Computational fuzzy conductors can be converted to computational fuzzy extractors using standard techniques~(see \apref{sec:further defs}).
The following theorem states the construction is a computational fuzzy conductor~(proof in \apref{sec:construction analysis}).
\begin{theorem}
\label{thm:main thm first cons}
Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block sources over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.  Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\gamma$.  Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs. Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec}=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
\end{theorem}

\subsection{More errors than entropy?}
\label{sec:discussion}
In this section, we show that \consref{cons:first construction} can support distributions with more errors than entropy.
We first calculate the size of the Hamming ball.
\[
\log |B_t| = \log \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i> \log {\gamma \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\gamma\choose t}
\]
The simplest type of unguessable block source is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).  For this type of source the entropy is $\Hoo(W) = \gamma\omega(\log n)$.  This yields:
\[
\text{\# errors} - \text{entropy} = \log |B_t| -  \Hoo(W)  >\left( \Theta(t\log |\mathcal{Z}|) + \log {\gamma \choose t}\right) -  \gamma \omega(\log n) .
\]
When $t =\Theta(\gamma)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then the construction supports more errors than entropy. Furthermore, the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\gamma)$).

@@

\subsection{Reusability Fuzzy Extractors}
\label{sec:comparing reusability}

>>>>

\def\shownotes{0}
\def\blinded{1}
\def\lncs{1}

\ifnum\lncs=0
	\documentclass[11pt]{article}
	\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
	\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
	%\geometry{landscape}                % Activate for for rotated page geometry
	%\usepackage[parfill]{parskip}
	\usepackage{amsthm}
	\newtheorem{theorem}{Theorem}[section]
	\newtheorem{lemma}[theorem]{Lemma}
	\newtheorem{proposition}[theorem]{Proposition}
	\newtheorem{corollary}[theorem]{Corollary}
	\newtheorem{definition}[theorem]{Definition}
	\newtheorem{assumption}[theorem]{Assumption}
	\newtheorem{claim}[theorem]{Claim}
	\newtheorem{problem}[theorem]{Problem}
	\newtheorem{construction}[theorem]{Construction}

\else
	\documentclass[runningheads]{../Asiacrypt/llncs}
	\newtheorem{construction}{Construction}
	\renewcommand{\paragraph}[1]{\subsubsection{#1}}
\fi

\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsfonts}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{framed}
\usepackage{algpseudocode}

@@

\begin{table}
\begin{center}
\ifnum\lncs=0
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline
Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\end{tabular}
\else
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline \vspace{-3mm} \\
Construction \ref{cons:sampling} & high-entropy & any subconstant \ \ &  Sample-then-obfuscate \\
\ \ (reusable)& \ \ samples\\ \vspace{-3mm} \\
Construction \ref{cons:first construction}  & sparse high-entropy \ \  & constant &  Error-correct-and-obfuscate\\
& \ \ marginals\\ \vspace{-3mm} \\
Construction \ref{cons:info theoretic}   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\ \ (info-theoretic)\\
\hline\end{tabular}
\fi
\end{center}
%end centering
\caption{Summary of new constructions. \consref{cons:sampling} supports the widest class of sources, including the sources supported by the other two constructions, but tolerates fewer errors than the other two constructions.  \consref{cons:first construction} and \consref{cons:info theoretic} support incomparable classes of sources.}
\label{tab:upper bounds}
\end{table}

@@

We augment the first construction with error-correcting codes to obtain our second construction, which works for \emph{sources with sparse high-entropy marginals}: sources over large alphabets for which sufficiently many symbols have high entropy individually, but no independence among symbols is assumed. In this construction, we use single symbols of $w$ to lock up bits of a secret that we then transform into $r$. This construction tolerates a higher error rate than the first construction, but over a larger alphabet, where errors may be more likely.

Our third construction provides information-theoretic, rather than computational, security. It works for \emph{sparse block sources}. These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous symbols. It uses symbol-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies a standard fuzzy extractor to the resulting string.

@@

@@

It is seems plausible that in the standard model (without random oracles), specific cryptographic hash functions, if used in this construction, will provide the necessary security~\cite[Section 3.2]{canetti2008obfuscating}, \cite[Section 8.2.3]{dakdoukThesis}. 
Moreover, Bitansky and Canetti~\cite{bitansky2010strong}, building on the work of~\cite{canetti2008obfuscating,CKVW10}, show how to obtain composable digital lockers based on a strong version of the Decisional Diffie-Hellman assumption without random oracles.

@@

@@

\paragraph{Sources with High-Entropy Samples}
Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$. For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$\subsetEntropy$-entropy $\eta$-samples} if 
\ifnum\lncs=0
$\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ 
\else
\[
\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy
\]
\fi
for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$. This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$. However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate (since the property has to hold only on  average for random $j_1, \dots, j_\eta$, a sufficiently small fraction of low-entropy symbols in $W$ can be tolerated).

Such sources $W$ can arise naturally as a result of signal processing and discretization. For example, suppose we start with a high-entropy reading $x$ of some physical source, and obtain each symbol $w_i$ by applying a short-output condenser (e.g., a random projection followed by discretization) to $x$. 
Each subsequent element in the sequence $w_{j_1}, \dots, w_{j_\eta}$ will extract fresh entropy as long as there remains entropy in $x$ conditioned on the previous elements (by a simple conditional entropy argument).

\paragraph{The Sample-then-Obfuscate Construction}
The construction first chooses a random $r$ to be used as the output of the fuzzy extractor. It then samples a random subset of symbols $v_1=w_{j_1},..., w_{j_\eta}$ and creates a digital locker that hides $r$ using $v_1$ (We present and analyze the construction with uniformly random subsets; however, if necessary, it is possible to substantially decrease the required public randomness and the length of $p$ by using more sophisticated samplers. See~\cite{goldreich2011sample} for an introduction to samplers.) This process is repeated to produce some number $\ell$ of digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively. The use of the composable digital lockers allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$.  Composability also allows reusability.

\begin{construction}[Sample-then-Obfuscate]
\label{cons:sampling}
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source with $\subsetEntropy$-entropy $\eta$-samples, where each $W_j$ is over $\mathcal{Z}$.  Let $\ell$ be a parameter, to be determined later. 
Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for the family of digital lockers with $\kappa$-bit outputs. Define $\gen, \rep$ as:

\begin{center}
\begin{tabular}{c|c}
\ifnum\lncs=0
\begin{minipage}{3in}
\else
\begin{minipage}{2.3in}
\fi
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $r \overset{\$}\leftarrow \zo^\kappa$.
\item For $i=1,..., \ell$:
\begin{enumerate}[(i)]
\item Choose uniformly random distinct $1\le j_{i, 1},..., j_{i, \eta}\le \gamma$
\item Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
\item Set $\rho_i = \mathcal{O}(I_{v_i, r})$.
\item Set $p_i = \rho_i, (j_{i, 1},..., j_{i, \eta})$.
\end{enumerate}
\item Output $(r, p)$, where $p=p_1\dots p_\ell$.
\end{enumerate}
 \end{minipage}\ \  &
\ifnum\lncs=0
\begin{minipage}{3in}
\else
\begin{minipage}{2.2in}
\fi
\ \ \textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w'=w_1',..., w_\gamma', p = p_1\dots p_\ell)$
\item For $i=1,..., \ell$:
\begin{enumerate}[(i)]
\item Parse $p_i$ as $\rho_i, (j_{i, 1},..., j_{i, \eta})$.
\item Set $v_i' = w_{j_{i, 1}}',..., w_{j_{i, \eta}}'$.
\item Set $\rho_i(v_i') = r_i$.  If $r_i\neq \perp$ output $r_i$.
\end{enumerate}
\item Output $\perp$.
\end{enumerate}
\ifnum\lncs=0
\vspace{0.6in}
\fi
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\section{Construction for Sources with Sparse High-Entropy Marginals}
\label{sec:cor construction}
In this section, we consider an alternative construction that is particularly well suited to sources over large alphabets. It requires enough symbols individually to contain sufficient entropy, but does not require independence of symbols, or even ``fresh'' entropy from them. Unlike the previous construction, it tolerates a linear fraction of errors. However, it cannot work for small alphabets, and is not reusable.

\paragraph{Sources with Sparse High-Entropy Marginals} This construction works for distributions $W=W_1, ... ,W_\gamma$ over $\mathcal{Z}^\gamma $ in which enough symbols $W_j$ are unpredictable even after adaptive queries to equality oracles for other symbols. This quality of a distribution is captured in the following definition.

\begin{definition}
\label{def:block guessable}
Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
\begin{cases}
1 & w_j = w_j'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1, ... ,W_\gamma$ has $\beta$-sparse $\alpha$-entropy $q$-marginals if there exists a set $J\subset\{1,..., \gamma\}$ of size at least $\gamma -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
\[
\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

We show some examples of such sources in \apref{sec:characterize}.  In particular, any source $W$ where for all $j$, $\Hoo(W_j) \geq \omega(\log n)$~(but all symbols may arbitrarily correlated) is a source with sparse high-entropy marginals~(\clref{cl:all blocks entropy}).

\paragraph{The Error-Correct-and-Obfuscate Construction}
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.  Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of the output.

Before presenting the construction we provide some definitions from error correcting codes.
We use error-correct codes over $\{0,1\}^\gamma$ which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
Codes with $2^{\Theta(\gamma)}$ codewords and $t = \Theta(\gamma)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).  These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
}
\begin{definition}
\label{def:hamming z channel}
Let $e, c\in \zo^\gamma$ be vectors.  Let $x = \error(c, e)$ be defined as follows
\[x_i = \begin{cases} 1 & c_i=1 \vee e_i=1\\
0& \text{ otherwise}.\end{cases}\]
\end{definition}

\begin{definition}
A set $C$~(over $\zo^\gamma$) is a $(t, \delta_{code})$-Z code if there exists an efficient procedure $\decode$ such that \[\forall e \in \zo^\gamma | \weight(e)\le t, \Pr_{c\in C}[\decode(\error(c,e)) \neq c] \leq \delta_{code}.\]
\end{definition}

\begin{construction}[Error-Correct-and-Obfuscate]
\label{cons:first construction}
Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.  Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.  Let  $C\subset \zo^\gamma$ be $(t, \delta_{code})$-Z code.
We describe $\gen, \rep$ as follows:

\begin{center}
\begin{tabular}{c|c}
\ifnum\lncs=0
\begin{minipage}{3in}
\else
\begin{minipage}{2.25in}
\fi
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $c\leftarrow C$.
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item If $c_j = 0$: $p_j = \mathcal{O}(I_{w_j})$.
\item Else: $r_j \overset{\$}\leftarrow \mathcal{Z}$.
\subitem Let $p_j = \mathcal{O}(I_{r_j})$.
\end{enumerate}
\item Output $(c, p)$, where $p=p_1\dots p_\gamma$.
\end{enumerate}
 \end{minipage} \ \ &
\ifnum\lncs=0
\begin{minipage}{3in}
\else
\begin{minipage}{2.25in}
\fi
\ \ \textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item If $p_j(w_j') = 1$: set $c_j' = 0$.
\item Else: set $c_j' = 1$.
\end{enumerate}
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.15in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\noindent
As presented, \consref{cons:first construction} is not yet a computational fuzzy extractor.  The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).  However, we can show that $c$ looks like it has entropy to a computationally bounded adversary who knows $p$. Applying a randomness extractor with outputs over $\zo^\kappa$ (technically, an average-case computational randomness extractor) to $c$, and adding the extractor seed to $p$, will give us the desired fuzzy extractor. See \apref{sec:further defs} for the formal details.

\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.  By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function. Therefore, our construction is secure as long as enough symbols are unpredictable even after adaptive queries to equality oracles for individual symbols, which is exactly the property satisfied by sources with sparse high-entropy marginals.

The following theorem formalizes this intuition~(proof in \apref{sec:construction analysis}).
\begin{theorem}
\label{thm:main thm first cons}
Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
Let $\mathcal{W}$ be a family of sources with $\beta$-sparse $\alpha=\omega(\log n)$-entropy $q$-marginals over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.  Furthermore, let $C$ be a $(t, \delta_{code})$-Z code over $\mathcal{Z}^\gamma$.  Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs. Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec}=\ngl(n)$ such that \consref{cons:first construction}, followed by a $\kappa$-bit randomness extractor, is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
\end{theorem}

\paragraph{More Errors than Entropy?}
\label{sec:discussion}
In this section, we show that \consref{cons:first construction} can support distributions with more errors than entropy.
We first calculate the size of the Hamming ball.
\[
\log |B_t| = \log \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i> \log {\gamma \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\gamma\choose t}\,.
\]
The simplest type of a source with high-entropy marginals is where each symbol is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).  For this type of source the entropy is $\Hoo(W) = \gamma\omega(\log n)$.  This yields:
\[
\text{\# errors} - \text{entropy} = \log |B_t| -  \Hoo(W)  >\left( \Theta(t\log |\mathcal{Z}|) + \log {\gamma \choose t}\right) -  \gamma \omega(\log n) .
\]
When $t =\Theta(\gamma)$ and the entropy of each block is $o(\log |\mathcal{Z}|)$, then the construction supports more errors than entropy. Furthermore, the output entropy is $H_0(C) -\beta$~(if $C$ is a constant rate code, this is $\Theta(\gamma)$).

@@

\subsection{Reusability of Fuzzy Extractors}
\label{sec:comparing reusability}
